BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2017-04-07 Paper2/BOAST.tex
passe FD-BV affiliations

%% or include affiliations in footnotes:
\author{
   \IEEEauthorblockN{Brice Videau\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}, Kevin Pouget\IEEEauthorrefmark{1}\IEEEauthorrefmark{3}, Luigi Genovese\IEEEauthorrefmark{4}, Thierry Deutsch\IEEEauthorrefmark{4}, Dimitri Komatitsch\IEEEauthorrefmark{6}, Frédéric Desprez\IEEEauthorrefmark{1}\IEEEauthorrefmark{5}, Jean-François Méhaut\IEEEauthorrefmark{1}\IEEEauthorrefmark{3}}\\
   \IEEEauthorblockA{\IEEEauthorrefmark{1}Laboratoire d'Informatique de Grenoble}\\
   \IEEEauthorblockA{\IEEEauthorrefmark{2}Centre National de la Recherche Scientifique}\\
   \IEEEauthorblockA{\IEEEauthorrefmark{3}Université Grenoble Alpes}\\
   \IEEEauthorblockA{\IEEEauthorrefmark{4}CEA/INAC/MEM/L\_Sim}\\
   \IEEEauthorblockA{\IEEEauthorrefmark{5}Inria}\\
   \IEEEauthorblockA{\IEEEauthorrefmark{6}Aix Marseille Univ., CNRS, Centrale Marseille, LMA, Marseille, France.}
}

>>>>

%% or include affiliations in footnotes:
\author{
   \IEEEauthorblockN{Brice Videau\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}, Kevin Pouget\IEEEauthorrefmark{1}\IEEEauthorrefmark{3}, Luigi Genovese\IEEEauthorrefmark{4}\IEEEauthorrefmark{3}, Thierry Deutsch\IEEEauthorrefmark{4}\IEEEauthorrefmark{3}, Dimitri Komatitsch\IEEEauthorrefmark{6}, Frédéric Desprez\IEEEauthorrefmark{1}\IEEEauthorrefmark{5}, Jean-François Méhaut\IEEEauthorrefmark{1}\IEEEauthorrefmark{3}}\\
   \IEEEauthorblockA{\IEEEauthorrefmark{1}Laboratoire d'Informatique de Grenoble}\\
   \IEEEauthorblockA{\IEEEauthorrefmark{2}Centre National de la Recherche Scientifique}\\
   \IEEEauthorblockA{\IEEEauthorrefmark{3}Université Grenoble Alpes}\\
   \IEEEauthorblockA{\IEEEauthorrefmark{4}CEA/INAC/MEM/L\_Sim}\\
   \IEEEauthorblockA{\IEEEauthorrefmark{5}Inria}\\
   \IEEEauthorblockA{\IEEEauthorrefmark{6}Aix Marseille Univ., CNRS, Centrale Marseille, LMA, Marseille, France.}
}
